---
title: "Assignment_4"
author: "Bharadwaj"
output:
  pdf_document: default
  word_document: default
---
Loading the required libraries and data set
```{r}
library(tidyverse)
library(factoextra)
pharmaceutical_0data<-read.csv("C:/Users/CherRyY/Documents/R/dataset/Pharmaceuticals.csv")
pharmaceutical_data<-na.omit(pharmaceutical_0data)

```

Here we’ll be using the numerical variables (1 to 9) to cluster the 21 firms.
```{r}
row.names(pharmaceutical_0data)<-pharmaceutical_0data[,1]
Clustering_data<-pharmaceutical_0data[,3:11]
```
Scaling the data according to requirement
```{r}
set.seed(120)
ScaledData<-scale(Clustering_data)

```

Performing Kmeans clustering for random K values(trail and error)
```{r}
set.seed(143)
kmeans_2<-kmeans(ScaledData,centers = 2, nstart = 15)
kmeans_4<-kmeans(ScaledData,centers = 4, nstart = 15)
kmeans_8<-kmeans(ScaledData,centers = 8, nstart = 15)

plot_kmeans_2<-fviz_cluster(kmeans_2,data = ScaledData) + ggtitle("K=2")
plot_kmeans_4<-fviz_cluster(kmeans_4,data = ScaledData) + ggtitle("K=4")
plot_kmeans_8<-fviz_cluster(kmeans_8,data = ScaledData) + ggtitle("K=8")

plot_kmeans_2
plot_kmeans_4
plot_kmeans_8


```

to find best K suitable for clustering, we’ll use the WSS and silhouette method

```{r}
k_wss<-fviz_nbclust(ScaledData,kmeans,method="wss")
k_silhouette<-fviz_nbclust(ScaledData,kmeans,method="silhouette")
k_wss
k_silhouette
distance<-dist(ScaledData,metho='euclidean')
fviz_dist(distance)
```

Given a K value of 2 from the within-cluster sum of squares (wss) and a K value of 5 from the silhouette analysis, the choice is to opt for K equals 5. This decision is motivated by the aim to achieve a low sum of squares while ensuring effective separation within the clusters. Now, the next step is to conduct a K-means analysis to determine the optimal K for the given data.

```{r}
set.seed(143)
kmeans_5<-kmeans(ScaledData,centers = 5, nstart = 10)
kmeans_5
plot_kmeans_5<-fviz_cluster(kmeans_5,data = ScaledData) + ggtitle("K=5")
plot_kmeans_5

Clustering_data_1<-Clustering_data%>%
  mutate(Cluster_no=kmeans_5$cluster)%>%
  group_by(Cluster_no)%>%summarise_all('mean')
Clustering_data_1

```
Companies are grouped into following clusters:
Cluster_1= ABT,AHM,AZN,BMY,LLY,NVS,SGP,WYE
Cluster_2= BAY,CHTT,IVX
Cluster_3=AVE,ELN,MRX,WPI
Cluster_4=AGN,PHA
Cluster_5=GSK,JNJ,MRK,PFE
From the above clusters 
1.Cluster_1 comprizes companies with moderate returns on Equity and Investment
2.Cluster_2 Consists of Companies with Poor returns on Assets(ROA), Return on Equity (ROE), Low market Capitalization, and weak Asset turnover. This suggests that these Companies are Highly Risky 
3.Cluster_3 Includes Companies Similar to those in cluster 2 but with Slightly lower levels of risk
4.Cluster_4 Contains companies with very high price to earnings (P/E) ratios but extremely poor ROA and ROE, making them even riskier than those in cluster 2
5.Cluster_5 is made up of companies with Excellent market capitalization, ROE and ROA

```{r}
Clustering_data_2<- pharmaceutical_data[,12:14] %>% mutate(Clusters=kmeans_5$cluster)
ggplot(Clustering_data_2, mapping = aes(factor(Clusters), fill =Median_Recommendation))+geom_bar(position='dodge')+labs(x ='Clusters')
ggplot(Clustering_data_2, mapping = aes(factor(Clusters),fill = Location))+geom_bar(position = 'dodge')+labs(x ='Clusters')
ggplot(Clustering_data_2, mapping = aes(factor(Clusters),fill = Exchange))+geom_bar(position = 'dodge')+labs(x ='Clusters')


```

Upon scrutinizing the data, a discernible pattern emerges in the relationship between clusters and the 'Median Recommendation' variable. Cluster 3 tends to incline towards ratings ranging from "moderate buy" to "moderate sell," while Cluster 2 tends to endorse recommendations within the spectrum of "hold" to "moderate buy."

A more in-depth analysis of the geographical distribution of pharmaceutical companies reveals a concentration in the United States. However, there is no clear trend in their distribution, except for the noteworthy observation that a majority of these companies are listed on the New York Stock Exchange (NYSE). Notably, there is no evident correlation between clusters and their presence in specific stock markets.

By considering both return on assets and net market capitalization, we can assign names to these clusters, thereby providing a more comprehensive labeling of the groupings.

[It is done based net Market capitalization(size) and Return on Assets(money)]


Cluster 1: High_Million  


Cluster 2: Additional Tiny Penny


Cluster 3: Small Amounts of Money


Cluster 4: The Mid-Hundreds


Cluster 5: Extremely Large-Millions 